Parallelizing Linear Recurrent Neural Nets Over Sequence Length

### 2018-04-24 poster/main.tex
Small changes

\institute{Fill in institutes} % Institution(s)

@@

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------
\begin{block}{Background}
Large minibatches are necessary for computational performance but create large memory
requirements and damage model generalization ability.

@@

Given $x_t$, $\lambda_t$ can compute $h_t=\lambda_t h_{t-1} + x_t$ for $t=1\ldots T$ on $p$
processors in $O(T/p + \log(p))$ with the classic parallel scan algorithm. Backpropagation
of gradient can also be parallelized with the same algorithm.
\end{block}

\vspace{2ex}

@@

\begin{figure}
\includegraphics[width=1.0\linewidth]{cumsum.png}
\caption{Cumulative sum parallelized over 3 processors}
\end{figure}

>>>>

\institute{FILL IN INSTITUTES} % Institution(s)

@@

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------
\begin{block}{Introduction}
Large minibatches are necessary for computational performance but create large memory
requirements and damage model generalization ability.

@@

Given $x_t$, $\lambda_t$ can compute $h_t=\lambda_t h_{t-1} + x_t$ for $t=1\ldots T$ on $p$
processors in $O(T/p + \log(p))$ with the classic parallel scan algorithm. Backpropagation
of gradient can also be parallelized with the same algorithm. We implemented a parallel linear
recurrence operation in CUDA and integrated it with TensorFlow.
\end{block}

@@

\begin{figure}
\includegraphics[width=1.0\linewidth]{cumsum.png}
\caption{Example of parallelizing cumulative sum over 3 processors}
\end{figure}
